Coexistence with varying environmental filtering intensity

### 2018-08-14 env_intensity.Rmd
:construction: Compute realized growth rates
Co-authored-by: Rekyt <matthias.grenie@ens-lyon.fr>
Co-authored-by: pierredenelle <pierre.denelle@cefe.cnrs.fr>

@@

>>>>

### Compute growth rate

@@

```{r}
compute_realized_growth_rate = function(given_compo, given_patch) {
    compo_patch = given_compo[given_patch, , ]

    # Keep only species present at last timestep
    compo_patch[compo_patch[, 150] != 0,] %>%
        t() %>%
        as.data.frame() %>%
        rownames_to_column("time") %>%  # Add time
        # Compute actual growth rate
        mutate_at(vars(contains("species")), function(x) x/lag(x)) %>%
        tail(1) %>%
        select(-time) %>%
        # Rearrange dataset to be tidy
        gather("species", "real_growth_rate") %>%
        mutate(patch = given_patch)
}

real_growth_rate_df = lapply(paste0("patches", 1:patches), function(given_patch) {
    compute_realized_growth_rate(three_traits$RA20$compo, given_patch)
}) %>%
    bind_rows()

full_growth_df = sp_growth_df %>%
    left_join(real_growth_rate_df, by = c("species", "patch"))

ggplot(full_growth_df %>%
           filter(!is.na(real_growth_rate)), aes(growth_rate, real_growth_rate)) +
    geom_point() +
    labs(x = "Theoretical Growth Rate (only growth)",
         y = "Realized Growth Rate") +
    theme_bw()
```

The following chunk computes all growth rates over all scenarios:
```{r}
# For all scenarios compute theoretical growth for all species in all patches
scenar_growth = lapply(trait_types, function(scenario) {
    # For all species compute the theoretical growth rate
    apply(traits, 1, function(x) {
        # Loop over patches
        lapply(env, function(y) {
            env_curve(x, y, trait_weights = scenario, k = k, width = 10)
        })
    }) %>%
        # Rearrange lists into tidy data.frame
        lapply(function(given_list) {
            data.frame(patch = rep(names(given_list), sapply(given_list, length)),
                       theo_growth_rate = unlist(given_list))
        }) %>%
        bind_rows(.id = "species")
}) %>%
    bind_rows(.id = "scenario") %>%
    mutate(patch_optim = as.numeric(gsub("patches", "", patch))) %>%
    # Add species trait values
    inner_join(traits %>%
                   as.data.frame() %>%
                   rownames_to_column("species"),
               by = "species")

scenar_real_growth = lapply(three_traits, function(scenar_compo) {
  scenar_compo = scenar_compo$compo

  lapply(paste0("patches", 1:patches), function(given_patch) {
    compute_realized_growth_rate(scenar_compo, given_patch)
}) %>%
    bind_rows()
}) %>%
    bind_rows(.id = "scenario")

full_growth = scenar_growth %>%
    left_join(scenar_real_growth, by = c("scenario", "patch", "species"))
```

```{r plot_growth_theo_real}
ggplot(full_growth %>%
           filter(!is.na(real_growth_rate)), aes(theo_growth_rate, real_growth_rate)) +
    geom_point() +
    geom_smooth(method = "lm") +
    ggpmisc::stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label..,
                                            sep = "~~~")), formula = y ~ x,
                          parse = TRUE) +
    facet_grid(cols = vars(scenario)) +
    labs(x = "Theoretical Growth Rate (only growth)",
         y = "Realized Growth Rate") +
    theme_bw()
```
